\sysfull

### 2018-04-14 paper/background.tex
intellectually modtivating coala design

>>>>

\textbf{Intellectually Motivating the Design of \sys's Execution Model.}  
The challenge of \em{efficiently} executing a program under frequent power failures, lies in the fact the the program needs to be energy aware. This challenge becomes even bigger when \em{generality} is a design requirement and such the system must not require a specific hardware circuitry to offer its efficiency. \em{flexibility} is key for wide adaptation, therefore, \sys's execution model should not limit the programmer to a subset of the functionality of the underlying software  technology. \em{\sys champions an efficient, general, and flexible intermittent execution.}
